Community-Conditioned Language Models

### 2020-11-13 paper/paper.tex
small changes

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{pgfplots}
\usepackage{todonotes}
\usepackage{enumitem}
\usepackage{cleveref}
\renewcommand{\UrlFont}{\ttfamily\small}
\usepgfplotslibrary{groupplots}
\pgfplotsset{compat=1.16}

@@

We also note that the conditioned models perform differently across different communities---\
for some communities, perplexity of the conditioned models is a lot lower (Table~\ref{tab:model-ppls},\bn{is this ok took ``test'' out but made clear in the caption that it's the test set}%\jp{and training?}
whereas for others it is the same or even slightly higher.
\bn{TODO: talk about this in terms of mutual information instead?}
As an anecdotal observation, we note 
that communities where conditioning has the least effect
tend to be more organized around more ``general interest'' topics,
such as /r/relationships, where the subject matter is relevant to a broad
range of people. \bn{I really mean this as a quality of the topic, rather than the community itself.}% \jp{Is there a way to quantify general interest topics? Community size in terms of number of users?}
Conditioning the model on community has the most benefit
for narrower special-interest subreddits such as those organized
around a certain videogame, sports team, or subculture.

This makes sense intuitively, since communities with more niche topics
would tend to have more specialized vocabulary and speech patterns.\bn{i think it's ok---i've seen this broader sense used in academic papers}%\jp{can you say speech for written language?}

The pattern of how much the perplexity falls across different communities
is similar across architectures, but with some differences.\jp{Either say something specific here or move the whole paragraph to future work.}
It could be interesting to further investigate these differences in future work,
since it could reveal differences in the kind of linguistic variation the different
model architectures capture.

@@

The perplexity of a CCLM tells is a measure of linguistic complexity,
but it is not a measure of how linguistically \emph{specific} the
community is. However, the CCLM induces a latent 
a latent classifier induced by a CCLM, which we call a language-model-based community classifier
(LMCC). Indeed, using the Bayes theorem, we can turn a
CCLM into a LMCC: the probability that a given message $m$
belongs to a community $c_i$ can be calculated as follows:
\[P(c=c_i | m) = P(m | c_i)\frac {P(m)} {P(c=c_i)}\]
In the above,
$P(c=c_i)$ is the frequency of community $c_i$ in the dataset, and
$P(m | c_i)$ (the probability that a message $m$
belongs in a community $c_i$. ) is estimated by the CCLM. $P(m)$ is the absolute
probability of a message, which can be computed as
\[P(m) = \frac 1 {\sum_i P(c=c_i) P(m|c=c_i ) }\].

We can characterise the quality the LMCC by a confusion matrix
$C$, defined by $C_{ij} = P(c=c_i | m)$ for a random message $m$ in
community $c_j$.  That is:
\[C_{ij} = average_{m \in Messages(c_j)}(P(c=c_i | m))\].
As a sanity check, we observe that the diagonal dominates the matrix: on average the LMCC picks the right community for a message.

\jp{Is this test set or training set?}

%\begin{figure*}
%\begin{tikzpicture}
  %\confusiongroupplot{floats/lstm-3-1_comm_infer_confusion.csv}{floats/transformer-3-3_comm_infer_confusion.csv}
%\end{tikzpicture}
%\caption{LMCC confusion matrices for the best LSTM (left, $c=1$) and transformer (right, $c=3$) models.}
%\label{fig:confusion}
%\end{figure*}

@@

  %\begin{tikzpicture}
  %\pplscatter{lstm-3-1_lmcc}{lstm-3-1_cclm}
  %\end{tikzpicture}

@@

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{pgfplots}
\usepackage{todonotes}
\usepackage{enumitem}
\usepackage{cleveref}

\usepgfplotslibrary{groupplots}
\pgfplotsset{compat=1.16}

\renewcommand{\UrlFont}{\ttfamily\small}

@@

We also note that the conditioned models perform differently across different communities---%
for some communities, perplexity of the conditioned models is a lot lower,\bn{is this ok? took ``test'' out but made clear in the caption that it's the test set}%\jp{and training?}
whereas for others it is the same or even slightly higher (Table~\ref{tab:model-ppls}).\bn{talk about this in terms of mutual information instead?}
As an informal observation, we note 
that across all the models we tested, 
communities where conditioning has the least effect
tend to be more organized around more ``general interest'' topics,
such as /r/relationships, where the subject matter is relevant to a broad
range of people. \bn{I really mean this as a quality of the topic, rather than the community itself, although the two are probably correlated}% \jp{Is there a way to quantify general interest topics? Community size in terms of number of users?}
Conditioning the model on community has the most benefit
for narrower special-interest subreddits such as those organized
around a certain videogame, sports team, or subculture.
This makes sense intuitively, since communities with more niche topics
would tend to have more specialized vocabulary and speech patterns.\bn{i think it's ok---i've seen this broader sense used in academic papers}%\jp{can you say speech for written language?}

@@

The perplexity of a CCLM gives us a measure of linguistic complexity,
but it is not a measure of how linguistically \emph{specific} the
community is. However, the CCLM induces a latent classifier,
which we call a language model-based community classifier
(LMCC). Using the Bayes theorem, we can turn a
CCLM into a LMCC: the probability that a given message $m$
belongs to a community $c_i$ is calculated as follows:
\[P(c=c_i | m) = P(m | c_i)\frac {P(m)} {P(c=c_i)}\]
In the above,
$P(c=c_i)$ is the frequency of community $c_i$ in the dataset, and
$P(m | c_i)$ (the probability that a message $m$
belongs in a community $c_i$. ) is estimated by the CCLM. $P(m)$ is the absolute
probability of a message, which can be computed as
\[P(m) = \frac 1 {\sum_i P(c=c_i) P(m|c=c_i ) }\].

We can characterise the quality the LMCC by a confusion matrix
$C$, defined by $C_{ij} = P(c=c_i | m)$ for a given message $m$ 
from the community $c_j$ portion of the test set.  That is:
\[C_{ij} = average_{m \in Messages(c_j)}(P(c=c_i | m))\].
As a sanity check, we observe that the diagonal dominates the matrix: on average the LMCC picks the right community for a message.

\begin{figure*}
\begin{tikzpicture}
  \confusiongroupplot{floats/lstm-3-1_comm_infer_confusion.csv}{floats/transformer-3-3_comm_infer_confusion.csv}
\end{tikzpicture}
\caption{LMCC confusion matrices for the best LSTM (left, $c=1$) and transformer (right, $c=3$) models.}
\label{fig:confusion}
\end{figure*}

@@

@@

% future work
The pattern of how much the perplexity falls across different communities
is similar across architectures, but with some differences.\jp{Either say something specific here or move the whole paragraph to future work.}
It could be interesting to further investigate these differences in future work,
since it could reveal differences in the kind of linguistic variation the different
model architectures capture.
